So you want to build a search engine?

### 2018-05-06 NetworkScience/Final/Final.tex
Hi

	\section{Introduction}
	So you want to build a search engine? Now there are a couple different types of search engines and not all search engines need to work the same, however there are two steps that are absolutely necessary for any searching to make sense. First you are going to need to have some set $A$ to search through and second you will need a search function $s:Q\to\pset{A}$\footnote{$\pset A$ is the power set of $A$.} where $Q$ is the set of all possible search queries. If we step away from mathematical formalities this makes sense as we simply are finding a way to match a search query to set of possibly results.

@@

	Now this web crawler works perfectly well, however it's going to be incredibly slow. The first step in optimizing this is always looking at

>>>>

	\section{Introduction}
	So you want to build a search engine? Now there are a couple different types of search engines and not all search engines need to work the same, however there are two steps that are absolutely necessary for any searching to make sense. First you are going to need to have some set $A$ to search through and second you will need a search function $s:Q\to\pset{A}$\footnote{$\pset A$ is the power set of $A$.} where $Q$ is the set of all possible search queries. If we step away from mathematical formalities, this makes sense, as we simply are finding a way to match a search query to set of possible results.

@@

	Now this web crawler works perfectly well, however it's going to be incredibly slow. The first step in optimizing this is always looking at what the slowest part is. Without even testing this program there is going to be a clear winner.
